### 2010-12-20 doc/tech_doc/a-rex/arex_tech_doc.tex
Fixing wrong attribute id in security attributes o a-rex

\begin{footnotesize}\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<Policy xmlns="http://www.nordugrid.org/schemas/policy-arc"
        PolicyId="policy:arex:example"
        CombiningAlg="Deny-Overrides">
   <Rule RuleId="knowarc.eu:serviceinfo" Effect="Permit">
      <Description>
         All who belongs to knowarc.eu VO can query information about service.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu</Subject>
      </Subjects>
      <Actions>
         <!-- AttributeId should be .../operation. But because of bug in A-REX this one is used. -->
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Info</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:admin" Effect="Permit">
      <Description>
         All developers belonging to knowarc.eu VO can manage service.
         This is useless rule because A-REX does not suport remote management.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=coredev</Subject>
      </Subjects>
      <Actions>
         <!-- AttributeId should be .../operation. But because of bug in A-REX this one is used. -->
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Admin</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:job" Effect="Permit">
      <Description>
         All testers of knowarc.eu VO can run jobs.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=testers</Subject>
      </Subjects>
      <Actions>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Create</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Modify</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Read</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:all" Effect="Permit">
      <Description>
         All superusers of knowarc.eu VO can do anything.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=superusers</Subject>
      </Subjects>
   </Rule>
</Policy>
\end{verbatim}
\end{footnotesize}

>>>>

\begin{footnotesize}\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<Policy xmlns="http://www.nordugrid.org/schemas/policy-arc"
        PolicyId="policy:arex:example"
        CombiningAlg="Deny-Overrides">
   <Rule RuleId="knowarc.eu:serviceinfo" Effect="Permit">
      <Description>
         All who belongs to knowarc.eu VO can query information about service.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu</Subject>
      </Subjects>
      <Actions>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/operation">Info</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:admin" Effect="Permit">
      <Description>
         All developers belonging to knowarc.eu VO can manage service.
         This is useless rule because A-REX does not suport remote management.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=coredev</Subject>
      </Subjects>
      <Actions>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/operation">Admin</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:job" Effect="Permit">
      <Description>
         All testers of knowarc.eu VO can run jobs.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=testers</Subject>
      </Subjects>
      <Actions>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Create</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Modify</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Read</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:all" Effect="Permit">
      <Description>
         All superusers of knowarc.eu VO can do anything.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=superusers</Subject>
      </Subjects>
   </Rule>
</Policy>
\end{verbatim}
\end{footnotesize}
